Supporting Information

### 2021-08-31 supplement/supplement-main.Rmd
fixes to install

---
title: "Supporting Information"
subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: pnas.csl
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

>>>>

---
title: "Supporting Information"
subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: pnas.csl
figsintext : yes
always_allow_html: true
header-includes:
  - \usepackage{float}
  - \usepackage{setspace}\doublespacing
---
